### 2011-02-25 trunk/deliverables/D5_2/fast_d5_2_3.tex
added brief appendix for D5.2.3
git-svn-id: https://svn.forge.morfeo-project.org/fast-fp7project@1297 d8b0c59b-6544-0410-94d9-83a5658a058e

\newcommand\deliverableNumber{D5.2.2}
\newcommand\deliverableTitle{Prototype Semantic Catalogue for Screen-Flow Gadgets and Back-End Services}
\newcommand\deliverableTitleShort{FAST Catalogue}
\newcommand\workpackageNumber{5}
\newcommand\workpackageTitle{Semantic catalogue of screen-flow resources and back-end Web Services}
\newcommand\authorOne{Ismael Rivera, NUIG}
\newcommand\authorTwo{Author 2}
\newcommand\authorThree{Author 3}
\newcommand\authorFour{Author 4}
\newtheorem{example}{\emph{Example}}

\begin{document}
% explicit hyphenations
\hyphenation{RDF-Re-po-si-to-ry}
\hyphenation{name-space}

@@

%\begin{minipage}[p]{15cm}
	\begin{center}
		\includegraphics{images/FAST_logo}\\
		\vspace{1cm}
		{\LARGE{\sffamily \emph{FAST AND ADVANCED STORYBOARD TOOLS}}}\\
		\vspace{0.5cm}
		{\LARGE \sffamily \emph{FP7-ICT-2007-1-216048}}\\
		\vspace{0.5cm}
		{\LARGE \sffamily \emph{http://fast.morfeo-project.eu}}\\
		\vspace{4cm}
		{\LARGE \sffamily \textbf{Deliverable \deliverableNumber}}\\
		\vspace{0.5cm}
		{\LARGE \sffamily \textbf{\deliverableTitle}}\\
		\vspace{2cm}
		{\large \sffamily \authorOne}\\
		\vspace{0.5cm}
		\vfill
		{\large \sffamily Date: 19/02/2010}\\
		\vspace{1cm}
		{\sffamily FAST is partially funded by the E.C. (grant code: FP7-ICT-2007-1-216048).}

@@

\begin{small}
\begin{tabular}{|l|l|l|p{7.5cm}|}
\hline
\rowcolor{fast@lightgrey}\textcolor{white}{\textbf{Rev. No.}} &
                         \textcolor{white}{\textbf{Date}} &
                         \textcolor{white}{\textbf{Author (Partner)}} &
                         \textcolor{white}{\textbf{Change description}}\\ \hline
1.0 & 20/02/2009 & Ismael Rivera (NUIG) & First version of the deliverable \\ \hline
2.0 & 19/02/2010 & Ismael Rivera (NUIG) & Second version of the deliverable \\ \hline
\end{tabular}
\end{small}

@@

Because D5.2 is a pure software deliverable, the sole role of this document is to function as a starting point for further information about the catalogue. Nevertheless, the deliverable D5.1 is aimed to fulfil this purpose, so for any further information such as where the code of the catalogue can be found, installation instructions, system requirements, a overview of the catalogue architecture or a detailed API, please read \cite{palaguita2010_usermanual}.

>>>>

\newcommand\deliverableNumber{D5.2.3}
\newcommand\deliverableTitle{Prototype Semantic Catalogue for Screen-Flow Gadgets and Back-End Services}
\newcommand\deliverableTitleShort{FAST Catalogue}
\newcommand\workpackageNumber{5}
\newcommand\workpackageTitle{Semantic catalogue of screen-flow resources and back-end Web Services}
\newcommand\authorOne{Ismael Rivera, NUIG}
\newcommand\authorTwo{Author 2}
\newcommand\authorThree{Author 3}
\newcommand\authorFour{Author 4}
\newtheorem{example}{\emph{Example}}

\begin{document}
% explicit hyphenations
%\hyphenation{RDF-Re-po-si-to-ry}
%\hyphenation{name-space}

@@

%\begin{minipage}[p]{15cm}
	\begin{center}
		\includegraphics{images/FAST_logo}\\
		\vspace{1cm}
		{\LARGE{\sffamily \emph{FAST AND ADVANCED STORYBOARD TOOLS}}}\\
		\vspace{0.5cm}
		{\LARGE \sffamily \emph{FP7-ICT-2007-1-216048}}\\
		\vspace{0.5cm}
		{\LARGE \sffamily \emph{http://fast.morfeo-project.eu}}\\
		\vspace{4cm}
		{\LARGE \sffamily \textbf{Deliverable \deliverableNumber}}\\
		\vspace{0.5cm}
		{\LARGE \sffamily \textbf{\deliverableTitle}}\\
		\vspace{2cm}
		{\large \sffamily \authorOne}\\
		\vspace{0.5cm}
		\vfill
		{\large \sffamily Date: 25/02/2011}\\
		\vspace{1cm}
		{\sffamily FAST is partially funded by the E.C. (grant code: FP7-ICT-2007-1-216048).}

@@

\begin{small}
\begin{tabular}{|l|l|l|p{7.5cm}|}
\hline
\rowcolor{fast@lightgrey}\textcolor{white}{\textbf{Rev. No.}} &
                         \textcolor{white}{\textbf{Date}} &
                         \textcolor{white}{\textbf{Author (Partner)}} &
                         \textcolor{white}{\textbf{Change description}}\\ \hline
1.0 & 20/02/2009 & Ismael Rivera (NUIG) & First version of the deliverable \\ \hline
2.0 & 19/02/2010 & Ismael Rivera (NUIG) & Second version of the deliverable \\ \hline
3.0 & 25/02/2011 & Ismael Rivera (NUIG) & Third version of the deliverable \\ \hline
\end{tabular}
\end{small}

@@

Because D5.2 is a pure software deliverable, the sole role of this document is to function as a starting point for further information about the catalogue. Nevertheless, the deliverable D5.1 is aimed to fulfil this purpose, so for any further information such as where the code of the catalogue can be found, installation instructions, system requirements, a overview of the catalogue architecture or a detailed API, please read \cite{palaguita2011_usermanual}.
